Glasgow Hackerspace CIC Articles of Association

### 2024-03-20 articles.tex
Fix duplicated section and add definitions of terms to end

\documentclass[12pt]{article}
%\usepackage[scaled]{helvet}
%\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage[a4paper, margin=0.5in]{geometry}
% \usepackage{graphicx} % Required for inserting images
\usepackage{hang}
% \usepackage{endnotes}
\usepackage[indentafter]{titlesec}
\usepackage{titletoc}
\usepackage{etoolbox}
\usepackage[singlespacing]{setspace}
\usepackage{changepage}
\usepackage{ragged2e}

@@

@@

% The following sub-section is highlighted in red in template: Obviously fundamental to C.I.C. operation!
\subsection{Community Interest Company}
\subsubsection[Community Interest Company]{\textcolor{\fakecolour}{The Company is to be a community interest company.}}
% The following sub-section is highlighted in red in template: Fundamental to C.I.C. operation!
\subsection{Asset Lock}
  \subsubsection[Full Consideration of Assets]{\textcolor{\fakecolour}{The Company shall not transfer any of its assets other than for full consideration.}}\label{subsubsubsection:fullconsideration}
  \subsubsection[Specifics of Full Consideration of Assets]{\textcolor{\fakecolour}{Provided the conditions in \fancyref{subsubsection:metaassetrestr} are satisfied, \fancyref{subsubsubsection:fullconsideration} shall not apply to:}}\label{subsubsection:transferrestrictions}
  \begin{subindentlist}
    \item [(a)] \textcolor{\fakecolour}{the transfer of assets to any specified asset-locked body, or (with the consent of the Regulator) to any other asset-locked body; and}
    \item [(b)] \textcolor{\fakecolour}{The conditions are that the transfer of assets must comply with any restrictions on the transfer of assets for less than full consideration which may be set out elsewhere in the Memorandum and Articles of the Company.}
  \end{subindentlist}
  \subsubsection[Conditions of Transfer of Assets]{The conditions are that the transfer of assets must comply with any restrictions on the transfer of assets for less than full consideration which may be set out elsewhere in the Memorandum and Articles of the Company.}\label{subsubsection:metaassetrestr}
% The following sub-section is not highlighted in red, but don't remove this, as it's fundamental to the space's model!
\subsection{Not For Profit}
\subsubsection[Investiture of Assets or Surplus in Community]{The Company is not established or conducted for private gain: any surplus or assets are
used principally for the benefit of the community.}

@@

\subsection{Participation in Directors' Meetings}
\subsubsection[Specifics of Participation in Directors' Meetings]{Subject to the Articles, Directors participate in a Directors' meeting, or part of a Directors' meeting, when:}
\begin{subindentpara}
  \item the meeting has been called and takes place in accordance with the Articles; and
  \item they can each communicate to the others any information or opinions they have on any particular item of the business of the meeting.
\end{subindentpara}
\subsubsection[Location of Participation in Director's Meetings is Irrelevant]{In determining whether Directors are participating in a Directors' meeting, it is irrelevant where any Director is or how they communicate with each other.}
\subsubsection[Nominal Location of a Meeting is at Directors' Discretion]{If all the Directors participating in a meeting are not in the same place, they may decide that the meeting is to be treated as taking place wherever any of them is.}
\subsubsection[Directors' May Authorise Any Person to Speak at a Meeting]{The board may, at its discretion, allow any person to attend and speak at a board meeting notwithstanding that they are not a director, but on the basis that they must not participate in decision-making.}

@@

% The following sub-section is highlighted in red in template:
\subsection{Decision-Making at Directors' Meetings}
  \subsubsection[Majority Voting at Directors' Meetings]{\textcolor{\fakecolour}{Questions arising at a Directors' meeting shall be decided by a majority of votes.}}
  \subsubsection[One Vote per Director at Directors' Meetings]{\textcolor{\fakecolour}{In all proceedings of Directors each Director must not have more than one vote.}}
\subsection{Decisions without a Meeting}\label{subsubsection:withoutmeeting}
\subsubsection[Directors' Unanimous Decisions by Other Means]{The Directors may take a unanimous decision without a Directors' meeting by indicating to each other by any means, including without limitation by Electronic Means, that they share a common view on a matter. Such a decision may, but need not, take the form of a resolution in Writing, copies of which have been signed by each Director or to which each Director has otherwise indicated agreement in Writing.}\label{subsubsubsection:unanimous}

@@

\subsection{Becoming a Member}
\subsubsection[First Members of the Company]{\textcolor{\fakecolour}{The subscribers to the Memorandum are the first Members of the Company.}}
\subsubsection[Members Are Admitted in Accordance with Articles]{\textcolor{\fakecolour}{Such other persons as are admitted to membership in accordance with the Articles shall be Members of the Company.}}
\subsubsection[Potential Members Must Be Approved by Directors]{\textcolor{\fakecolour}{No person shall be admitted a member of the Company unless they are approved by the Directors.}}
\subsubsection[Potential Members Must Apply for Membership]{\textcolor{\fakecolour}{Every person who wishes to become a Member shall deliver to the Company an application for membership in such form (and containing such information) as the Directors require and executed by the Member.}} % todo is this executed by the member? this was him or her before
\subsubsection[Directors Must notify Potential Members of Decision]{The Directors must notify each applicant for membership promptly (in Writing, including by Electronic Means) of its decision on whether or not to admit them to membership.} % Not red in original document
\subsubsection[Members May Not Be Organisations]{Members must be a physical person. Organisations are not eligible for membership.} % Not red in template

@@

\subsection{Termination of Membership}
\subsubsection[Membership Non-Transferable]{Membership is not transferable to anyone else.}
\subsubsection[Specifics of Termination of Membership]{Membership is terminated if:}
\begin{subindentpara}
    \item \textcolor{\fakecolour}{the Member dies or ceases to exist;}
    \item \textcolor{\fakecolour}{otherwise in accordance with the Articles;}
    \item the Member fails to pay the membership subscription for more than 3 months, and has not been granted an exemption by the Directors;
    \item the Member notifies the Hackerspace, via any means on which a director may be reached (in writing, including by Electronic Means) that they wish to cease to be a member; in which case, the Member ceases to be a Member from the time when the notice is received;
    \item the Member is expelled by way of a resolution passed by not less than two thirds of those present and voting at a general meeting, providing the following procedures have been observed: 
    \begin{subindentpara} % Note initial indentation of this child indented paragraph section may go too far. Largely unimportant, but note it inherits absolute indentation of regular hanging paragraphs from the margin.
        \item at least 21 days notice of the intention to propose the resolution must be given to the Member concerned,  specifying the grounds for the proposed expulsion; or
        \item the Member concerned will be entitled to be heard on the resolution at the general meeting at which the resolution is proposed
    \end{subindentpara}
    \item or;
    \item the Directors may temporarily suspend any Member from access to the Hackerspace's resources, if the behaviour of that Member is deemed by the Directors to be unacceptable to the Hackerspace. Suspension will continue until either the Directors reverse the suspension, or an expulsion resolution is heard. The suspended Member has the right to propose an expulsion resolution. A Member expelled by such a resolution will nevertheless remain liable to pay to the Company any subscription or other sum owed by that Member.
\end{subindentpara}
\subsubsection[Return of Keys upon Membership Termination]{Upon ceasing to be a Member, all means of access to the Hackerspace, including but not limited to keys and access tokens, must be returned to the Hackerspace.}

@@

\subsection{Chairing General Meetings}
\subsubsection[A Director Chairs a General Meeting]{A Director nominated by the Directors will preside as chair of a general meeting. If there is only one Director present and willing to act, they shall be chair of the meeting.} \label{subsubsection:nomchair}
\subsubsection[Members May Elect Chair in Absence of Suitable Director]{If no Director is willing to act as chair of the meeting, or if no Director is present within half an hour after the time appointed for holding the meeting, the members present in person or by proxy and entitled to vote must choose one of their number to be chair of the meeting, save that a proxy holder who is not a member entitled to vote shall not be entitled to be appointed chair of the meeting.}

@@

\subsection{Votes}
\subsubsection[Maximum One Vote in Show of Hands]{On a vote on a resolution on a show of hands at a meeting every person present in person (whether a member or a proxy for a member) and entitled to vote shall have a maximum of one vote.}
\subsubsection[Maximum One Vote on Resolution on Poll]{On a vote on a resolution on a poll at a meeting every member present in person or by proxy shall have one vote.}
\subsubsection[No Casting Vote for Meeting Chair]{In the case of an equality of votes, whether on a show of hands or on a poll, the chair of the meeting shall not be entitled to a casting vote in addition to any other vote they may have.}
\subsubsection[Member May Not Vote Unless All Monies Payable Paid]{No member shall be entitled to vote at any general meeting unless all monies presently payable by that member to the Company have been paid.}
\subsubsection[Votes on Expulsion/Termination by Secret Ballot Only]{Any resolution concerning expulsion or termination of a membership must be taken by secret ballot.}

@@

\subsection{Content of Proxy Notices}
\subsubsection[Specifics of Content of Proxy Notices]{Proxies may only validly be appointed by a notice in writing (a ``Proxy Notice'') which:}
\begin{subindentlist}
    \item [(a)] states the name of the member appointing the proxy;
    \item [(b)] identifies the person appointed to be that member's proxy and the general meeting in relation to which that person is appointed;
    \item [(c)] is signed by or on behalf of the member appointing the proxy, or is authenticated in such manner as the directors may determine; and
    \item [(d)] is delivered to the Company in accordance with the Articles and any instructions contained in the notice of the general meeting to which they relate.
\end{subindentlist}
\subsubsection[Form of Proxy Notices]{The Company may require Proxy Notices to be delivered in a particular form, and may specify different forms for different purposes.}
\subsubsection[Directions Contained in Proxy Notices]{Proxy Notices may specify how the proxy appointed under them is to vote (or that the proxy is to abstain from voting) on one or more resolutions.}
\subsubsection[Implication of Proxy Notices]{Unless a Proxy Notice indicates otherwise, it must be treated as:}
\begin{subindentlist}
    \item [(a)] allowing the person appointed under it as a proxy discretion as to how to vote on any ancillary or procedural resolutions put to the meeting; and
    \item [(b)] appointing that person as a proxy in relation to any adjournment of the general meeting to which it relates as well as the meeting itself.
\end{subindentlist}

@@

>>>>

\documentclass[12pt]{article}
%\usepackage[scaled]{helvet}
%\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage[a4paper, margin=0.5in]{geometry}
% \usepackage{graphicx} % Required for inserting images
\usepackage{hang}
% \usepackage{endnotes}
\usepackage[indentafter]{titlesec}
\usepackage{titletoc}
\usepackage{etoolbox}
\usepackage[singlespacing]{setspace}
\usepackage{changepage}
\usepackage[raggedrightboxes]{ragged2e}
\usepackage{longtable}

@@

% Tables
\setlength{\arrayrulewidth}{0.5mm}
\setlength{\tabcolsep}{18pt}
\renewcommand{\arraystretch}{1.5}

@@

% The following sub-section is highlighted in red in template: Obviously fundamental to C.I.C. operation!
\subsection{Community Interest Company}
\subsubsection[Community Interest Company]{\textcolor{\fakecolour}{The Company is to be a community interest company.}}
% The following sub-section is highlighted in red in template: Fundamental to C.I.C. operation!
\subsection{Asset Lock}
  \subsubsection[Full Consideration of Assets]{\textcolor{\fakecolour}{The Company shall not transfer any of its assets other than for full consideration.}}\label{subsubsubsection:fullconsideration}
  \subsubsection[Specifics of Full Consideration of Assets]{\textcolor{\fakecolour}{Provided the conditions in \fancyref{subsubsection:metaassetrestr} are satisfied, \fancyref{subsubsubsection:fullconsideration} shall not apply to:}}\label{subsubsection:transferrestrictions}
  \begin{subindentlist}
    \item [(a)] \textcolor{\fakecolour}{the transfer of assets to any specified asset-locked body, or (with the consent of the Regulator) to any other asset-locked body; and}
    \item [(b)] \textcolor{\fakecolour}{the transfer of assets made for the benefit of the community other than by way of a transfer of assets into an asset-locked body.}
  \end{subindentlist}
  \subsubsection[Conditions of Transfer of Assets]{\textcolor{\fakecolour}{The conditions are that the transfer of assets must comply with any restrictions on the transfer of assets for less than full consideration which may be set out elsewhere in the Memorandum and Articles of the Company.}}\label{subsubsection:metaassetrestr}
% The following sub-section is not highlighted in red, but don't remove this, as it's fundamental to the space's model!
\subsection{Not For Profit}
\subsubsection[Investiture of Assets or Surplus in Community]{The Company is not established or conducted for private gain: any surplus or assets are
used principally for the benefit of the community.}

@@

\subsection{Participation in Directors' Meetings}\label{subsection:dirmeetspart}
\subsubsection[Specifics of Participation in Directors' Meetings]{Subject to the Articles, Directors participate in a Directors' meeting, or part of a Directors' meeting, when:}
\begin{subindentpara}
  \item the meeting has been called and takes place in accordance with the Articles; and
  \item they can each communicate to the others any information or opinions they have on any particular item of the business of the meeting.
\end{subindentpara}
\subsubsection[Location of Participation in Director's Meetings is Irrelevant]{In determining whether Directors are participating in a Directors' meeting, it is irrelevant where any Director is or how they communicate with each other.}
\subsubsection[Nominal Location of a Meeting is at Directors' Discretion]{If all the Directors participating in a meeting are not in the same place, they may decide that the meeting is to be treated as taking place wherever any of them is.}
\subsubsection[Directors' May Authorise Any Person to Speak at a Meeting]{The board may, at its discretion, allow any person to attend and speak at a board meeting notwithstanding that they are not a director, but on the basis that they must not participate in decision-making.}

@@

% The following sub-section is highlighted in red in template:
\subsection{Decision making at a meeting}
  \subsubsection[Majority Voting at Directors' Meetings]{\textcolor{\fakecolour}{Questions arising at a Directors' meeting shall be decided by a majority of votes.}}
  \subsubsection[One Vote per Director at Directors' Meetings]{\textcolor{\fakecolour}{In all proceedings of Directors each Director must not have more than one vote.}}
\subsection{Decisions without a Meeting}\label{subsubsection:withoutmeeting}
\subsubsection[Directors' Unanimous Decisions by Other Means]{The Directors may take a unanimous decision without a Directors' meeting by indicating to each other by any means, including without limitation by Electronic Means, that they share a common view on a matter. Such a decision may, but need not, take the form of a resolution in Writing, copies of which have been signed by each Director or to which each Director has otherwise indicated agreement in Writing.}\label{subsubsubsection:unanimous}

@@

\subsection{Becoming a member}
\subsubsection[First Members of the Company]{\textcolor{\fakecolour}{The subscribers to the Memorandum are the first Members of the Company.}}
\subsubsection[Members Are Admitted in Accordance with Articles]{\textcolor{\fakecolour}{Such other persons as are admitted to membership in accordance with the Articles shall be Members of the Company.}}
\subsubsection[Potential Members Must Be Approved by Directors]{\textcolor{\fakecolour}{No person shall be admitted a member of the Company unless they are approved by the Directors.}}
\subsubsection[Potential Members Must Apply for Membership]{\textcolor{\fakecolour}{Every person who wishes to become a Member shall deliver to the Company an application for membership in such form (and containing such information) as the Directors require and executed by the Member.}} % todo is this executed by the member? this was him or her before
\subsubsection[Directors Must notify Potential Members of Decision]{The Directors must notify each applicant for membership promptly (in Writing, including by Electronic Means) of its decision on whether or not to admit them to membership.} % Not red in original document
\subsubsection[Members May Not Be Organisations]{Members must be a physical person. Organisations are not eligible for membership.} % Not red in template

@@

\subsection{Termination of Membership}
\subsubsection[Membership Non-Transferable]{\textcolor{\fakecolour}{Membership is not transferable to anyone else.}}
\subsubsection[Specifics of Termination of Membership]{\textcolor{\fakecolour}{Membership is terminated if:}}
\begin{subindentpara}
    \item \textcolor{\fakecolour}{the Member dies or ceases to exist;}
    \item \textcolor{\fakecolour}{otherwise in accordance with the Articles;}
    \item the Member fails to pay the membership subscription for more than 3 months, and has not been granted an exemption by the Directors;
    \item the Member notifies the Hackerspace, via any means on which a director may be reached (in writing, including by Electronic Means) that they wish to cease to be a member; in which case, the Member ceases to be a Member from the time when the notice is received;
    \item the Member is expelled by way of a resolution passed by not less than two thirds of those present and voting at a general meeting, providing the following procedures have been observed: 
    \begin{subindentpara} % Note initial indentation of this child indented paragraph section may go too far. Largely unimportant, but note it inherits absolute indentation of regular hanging paragraphs from the margin.
        \item at least 21 days notice of the intention to propose the resolution must be given to the Member concerned,  specifying the grounds for the proposed expulsion; or
        \item the Member concerned will be entitled to be heard on the resolution at the general meeting at which the resolution is proposed
    \end{subindentpara}
    \item or;
    \item the Directors may temporarily suspend any Member from access to the Hackerspace's resources, if the behaviour of that Member is deemed by the Directors to be unacceptable to the Hackerspace. Suspension will continue until either the Directors reverse the suspension, or an expulsion resolution is heard. The suspended Member has the right to propose an expulsion resolution. A Member expelled by such a resolution will nevertheless remain liable to pay to the Company any subscription or other sum owed by that Member.
\end{subindentpara}
\subsubsection[Return of Keys upon Membership Termination]{Upon ceasing to be a Member, all means of access to the Hackerspace, including but not limited to keys and access tokens, must be returned to the Hackerspace.}

@@

\subsection{Chairing General Meetings}\label{subsection:chairgen}
\subsubsection[A Director Chairs a General Meeting]{A Director nominated by the Directors will preside as chair of a general meeting. If there is only one Director present and willing to act, they shall be chair of the meeting.} \label{subsubsection:nomchair}
\subsubsection[Members May Elect Chair in Absence of Suitable Director]{If no Director is willing to act as chair of the meeting, or if no Director is present within half an hour after the time appointed for holding the meeting, the members present in person or by proxy and entitled to vote must choose one of their number to be chair of the meeting, save that a proxy holder who is not a member entitled to vote shall not be entitled to be appointed chair of the meeting.}

@@

\subsection{Votes}\label{subsection:votes}
\subsubsection[Maximum One Vote in Show of Hands]{On a vote on a resolution on a show of hands at a meeting every person present in person (whether a member or a proxy for a member) and entitled to vote shall have a maximum of one vote.}
\subsubsection[Maximum One Vote on Resolution on Poll]{On a vote on a resolution on a poll at a meeting every member present in person or by proxy shall have one vote.}
\subsubsection[No Casting Vote for Meeting Chair]{In the case of an equality of votes, whether on a show of hands or on a poll, the chair of the meeting shall not be entitled to a casting vote in addition to any other vote they may have.}
\subsubsection[Member May Not Vote Unless All Monies Payable Paid]{No member shall be entitled to vote at any general meeting unless all monies presently payable by that member to the Company have been paid.}
\subsubsection[Votes on Expulsion/Termination by Secret Ballot Only]{Any resolution concerning expulsion or termination of a membership must be taken by secret ballot.}

@@

\subsection{Content of Proxy Notices}\label{subsection:proxycont}
\subsubsection[Specifics of Content of Proxy Notices]{Proxies may only validly be appointed by a notice in writing (a ``Proxy Notice'') which:}
\begin{subindentlist}
    \item [(a)] states the name of the member appointing the proxy;
    \item [(b)] identifies the person appointed to be that member's proxy and the general meeting in relation to which that person is appointed;
    \item [(c)] is signed by or on behalf of the member appointing the proxy, or is authenticated in such manner as the directors may determine; and
    \item [(d)] is delivered to the Company in accordance with the Articles and any instructions contained in the notice of the general meeting to which they relate.
\end{subindentlist}
\subsubsection[Form of Proxy Notices]{The Company may require Proxy Notices to be delivered in a particular form, and may specify different forms for different purposes.}
\subsubsection[Directions Contained in Proxy Notices]{Proxy Notices may specify how the proxy appointed under them is to vote (or that the proxy is to abstain from voting) on one or more resolutions.}
\subsubsection[Implication of Proxy Notices]{Unless a Proxy Notice indicates otherwise, it must be treated as:}
\begin{subindentlist}
    \item [(a)] allowing the person appointed under it as a proxy discretion as to how to vote on any ancillary or procedural resolutions put to the meeting; and
    \item [(b)] appointing that person as a proxy in relation to any adjournment of the general meeting to which it relates as well as the meeting itself.
\end{subindentlist}

@@

\setcounter{section}{0}
\setcounter{subsection}{0}

\newpage\section*{\huge{Schedule}}
\addcontentsline{toc}{section}{Schedule}
\section*{\huge{Interpretation}}

\subsection*{Defined terms}
\subsection{\mdseries\normalsize{In the Articles, unless the context requires otherwise, the following terms shall have the following meanings:}}

%\begin{tabular}{p{1.5in} p{34em}}
\begin{longtable}[p]{ p{1.5in} p{30em} }
{\bfseries{Term}} & {\bfseries{Meaning}} \\
  ``Address'' & includes a number or address used for the purposes of sending or receiving Documents by Electronic Means; \\
  ``Articles'' & the Company's articles of association \\
  ``Authorised Representative'' & means any individual nominated by a Member Organisation to act as its representative at any meeting of the Company in accordance with \fancyref{subsection:votes} \\
  ``asset-locked body'' & means (i) a community interest company, a charity  or a Permitted Industrial and Provident Society; or (ii) a body established outside the United Kingdom that is equivalent to any of those; \\
  ``bankruptcy'' & includes individual insolvency proceedings in a jurisdiction other than England and Wales or Northern Ireland which have an effect similar to that of bankruptcy; \\
  ``chairman of the meeting'' & has the meaning given in \fancyref{subsection:chairgen}; \\
  ``Circulation Date'' & in relation to a written resolution, has the meaning given to it in the Companies Acts; \\
  ``Clear Days'' & in relation to the period of a notice, that period excluding the day when the notice is given or deemed to be given and the day for which it is given or on which it is to take effect; \\
  ``community'' & is to be construed in accordance with accordance with Section 35(5) of the Company’s (Audit) Investigations and Community Enterprise) Act 2004; \\
  ``Companies Acts'' & means the Companies Acts (as defined in Section 2 of the Companies Act 2006), in so far as they apply to the Company; \\
  ``Company'' & Glasgow Hackerspace CIC \\
  ``Conflict of Interest'' & any direct or indirect interest of a Director (whether personal, by virtue of a duty of loyalty to another organisation or otherwise) that conflicts, or might conflict with the interests of the Company; \\
  ``Director'' & a director of the Company, and includes any person occupying the position of director, by whatever name called; \\
  ``Document'' & includes, unless otherwise indicated, any Document sent or supplied in Electronic Form; \\
  ``Electronic Form'' and ``Electronic Means'' & have the meanings respectively given to them in Section 1168 of the Companies Act 2006; \\
  ``Hard Copy Form'' & has the meaning given to it in the Companies Act 2006; \\
  ``Memorandum'' & the Company’s memorandum of association; \\
  ``paid'' & means paid or credited as paid; \\
  ``participate'' & in relation to a Directors’ meeting, has the meaning given in \fancyref{subsection:dirmeetspart}; \\
  ``Permitted Industrial and Provident Society'' & an industrial and provident society which has a restriction on the use of its assets in accordance with Regulation 4 of the Community Benefit Societies (Restriction on Use of Assets) Regulations 2006 or Regulation 4 of the Community Benefit Societies (Restriction on Use of Assets) Regulations (Northern Ireland) 2006; \\
  ``Proxy Notice'' & has the meaning given in \fancyref{subsection:proxycont}; \\

  ``the Regulator'' & means the Regulator of Community Interest Companies; \\
  ``Secretary'' & the secretary of the Company (if any); \\
  ``specified'' & means specified in the memorandum and articles of association of the Company for the purposes of this paragraph; \\
  ``subsidiary'' & has the meaning given in section 1159 of the Companies Act 2006; \\
  ``transfer'' & includes every description of disposition, payment, release or distribution, and the creation or extinction of an estate or interest in, or right over, any property; and \\
  ``Writing'' & the representation or reproduction of words, symbols or other information in a visible form by any method or combination of methods, whether sent or supplied in Electronic Form or otherwise. \\  
\end{longtable}

\subsection{\mdseries\normalsize{Subject to clause 3 of this Schedule, any reference in the Articles to an enactment includes a reference to that enactment as re-enacted or amended from time to time and to any subordinate legislation made under it.}}
\subsection{\mdseries\normalsize{Unless the context otherwise requires, other words or expressions contained in these Articles bear the same meaning as in the Companies Act 2006 as in force on the date when the Articles become binding on the Company.}}
